### 2016-04-06 Projects/DelCo_2012/Report/DelCo_2012.tex
Added description to 2 story CAFs results, new dir to gas exp dir for HRR calculations

Note that while there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, differences are not substantial. Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression. The first (hallway) suppression, an indirect attack, did a majority of the cooling in all of the tests. This illustrates the impact of gas cooling, indpendent of suppression agent. In several cases rekindling occured, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.

@@

@@

@@

>>>>

Note that while there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, differences are not substantial. Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression. The first (hallway) suppression, an indirect attack, did a majority of the cooling in all of the tests. This illustrates the impact of gas cooling, independent of suppression agent. In several cases rekindling occurred, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.

@@

There were 7 suppression tests conducted in the two story purpose-built structure. All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over puf padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to this fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor south door. The fires were intended to replicate room and contents basement fires typically seen within residential structures. Suppression occurred at the basement double doors of the structure. Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted.

@@

Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAFs tests conducted in the two story structure. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 1st floor level in front of the stairway door. These values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.

@@

Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, but the differences are not substantial. Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
